Randomization Examples using `nycflights13` `flights` data

### 2017-12-27 inst/doc/flights_examples.Rmd
add GoF

```{r}
prof_small %>%
  specify(drugs ~ NULL) %>% # alt: response = drugs
  hypothesize(null = "point", 
              p = c("never" = .7, "sometimes" = .25, "often" = .05)) %>%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "Chisq") %>% 
  visualize()
```

>>>>

```{r}
null <- fli_small %>%
  specify(response = origin) %>%
  hypothesize(null = "point", p = c("EWR" = .33, "JFK" = .33, "LGA" = .34)) %>% 
  generate(reps = 1000, type = "simulate") %>% 
  calculate(stat = "Chisq")
expected <- nrow(fli_small)/3
Chisq_hat <- fli_small %>%
  count(origin) %>%
  mutate(z = (n - expected)^2/expected) %>%
  summarize(sum(z)) %>%
  pull()
ggplot(null, aes(x = stat)) +
  geom_density() +
  geom_vline(xintercept = Chisq_hat, col = "red")
null %>%
  summarize(mean(stat > Chisq_hat)) 
```
